Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-20 outputs/paper/paper.Rmd
survey writing

The purpose of this survey is ~~

@@

## Questions
1. 
2. 
3.

@@

Thank you ~~

@@

# References

>>>>

The purpose of this survey is to further investigate the 2016 U.S presidential election. We are interested in more and specific opinions regarding factors you consider important to decide who to vote than what US GSS provided. If you are not a US citizen, please pretend you are, or imagine that having very similar candidates in your home country.

@@

## Questions

@@

Thank you for participating in our survey. If you have any questions please do not hesitate to contact us.
sangwoong.lee@maill.utoronto.ca and young.suk@mail.utoronto.ca

@@

# References
-- Smith, Tom W., Davern, Michael, Freese, Jeremy, and Morgan, Stephen L., General Social Surveys, 1972-2018 [machine-readable data file] /Principal Investigator, Smith, Tom W.; Co-Principal Investigators, Michael Davern, Jeremy Freese and Stephen L. Morgan; Sponsored by National Science Foundation. --NORC ed.-- Chicago: NORC, 2019.

-- U.S. Census Bureau (2021). Population estimates. Retrieved from https://www.census.gov/quickfacts/fact/table/US/PST045221.
